\section{Hawk}
In this section we introduce the digital signature scheme Hawk \cite{HawkSpec24}, which will later be the target for our cryptanalysis.
As mentioned in the introduction, Hawk is a lattice based signature scheme that shares some key points with that of NTRU-sign \cite{HHPSW03}, the target for the original HPP attack.
The first part of this chapter/section will give an introduction to how the Hawk scheme works on a high level. After this, the implementation of Hawk will be described, where much more detail about 
specific parts of the procedures will be given.

In this section, quite a few parts of Hawk as described in \cite{HawkSpec24} are left out due to the focus of this thesis. For example, Hawk utilizes compression of keys and signatures 
(which influence the key generation and signature generation procedures),
and some of their security considerations regarding a practical implementation is based on side channel attacks, both of which is not a concern in this thesis.
Moreover, their security analysis is based on experimental lattice reduction and security proofs of the underlying hard problems (namely the \textit{Lattice Isomorphism Problem} and 
the \textit{One More Shortest Vector Problem}), which, again, is not the focus of this thesis. 

% Perhaps the most notable similarity is the algebraic structure of private key $\mat{B}$. Recall that in NTRU, polynomials are defined 
% over $\bb{Z}[X] / (X^n - 1)$, whereas in Hawk they are defined over $\bb{Z}[X] / (X^n + 1)$.
% The private key in NTRU is defined as 
% \[
%     \begin{bmatrix}
%         f_0 & f_1 & \cdots & f_{n-1} & g_0 & g_1 & \cdots & g_{n-1} \\
%         f_{n-1} & f_{0} & \cdots & \cdots & g_{n-1} & f_{0} & \cdots \\
%         \cdots \\ 
%         f_{1} & f_{2} & \cdots & f_{n-1} & f_0 & g_{1} & g_{2} & \cdots & g_{n-1} & g_0 \\
%         F_0 & F_1 & \cdots & F_{n-1} & G_0 & G_1 & \cdots & G_{n-1} \\
%         F_{n-1} & F_{0} & \cdots & \cdots & G_{n-1} & F_{0} & \cdots \\
%         \cdots \\ 
%         F_{1} & F_{2} & \cdots & F_{n-1} & F_0 & G_{1} & G_{2} & \cdots & G_{n-1} & G_0 \\
%     \end{bmatrix}
% \]
\subsection{Overview}
In Hawk, polynomials are defined over the cyclotomic number field $\mathcal{K}_n = \bb{Q}[X]/(X^n +1)$ which has the corresponding ring of integers
$\bb{Z}[X] / (X^n + 1)$. Such a polynomial $f \in \mathcal{K}_n$ can also be represented by a (column) vector of its coefficients in $\bb{Q}^n$, denoted $\mathsf{vec}(f)$, where the index of 
the coefficient corresponds to the power of $X$. 
\footnote{This is a polynomial representation that is frequent in programming implementations when a dedicated algebra library is not used.}
We define a mapping 
\[\mathsf{rot:} \mathcal{K}_n \rightarrow \bb{Q}^{n \times n}, \mathsf{rot}(f) = 
\begin{bmatrix} 
    \mathsf{vec}(f) & \mathsf{vec}(fX) & \mathsf{vec}(fX^2) & \cdots & \mathsf{vec}(fX^{n-1})
\end{bmatrix}    
\]
\todo{This should maybe be in the background section...}
which enables one to construct a matrix in $\bb{Q}^{n \times n}$ from a single polynomial in $\mathcal{K}_n$.
\todo{Define the integer polynomial ring $\bb{Z}[X] / (X^n +1)$}

The hash function used in Hawk is SHAKE256, an extendable output function (XOF) which enables arbitrary output length, unlike hash functions like SHA256 which 
has a static output size of 256 bits (as eight 32-bit words). This property is useful since SHAKE256 can be used in all three degrees of Hawk.

\subsection{Parameters}
Below is the parameters for Hawk degree 256, 512, and 1024. Note that this list only contains the relevant parameters for this overview, and that many parameters relevant to 
compression and decompression are omitted.

\begin{table}[h]
    \centering
    \caption{Parameter sets for \textbf{HAWK}. Note that key and signature sizes are specified in bytes.}
    \label{tab:hawk-parameters}
    \begin{tabular}{lccc}
        \toprule
        \textbf{Name} & \textbf{HAWK-256} & \textbf{HAWK-512} & \textbf{HAWK-1024} \\
        \midrule
        \multicolumn{1}{l}{Targeted security} & Challenge & NIST-I & NIST-V \\
        Bit security $\lambda$ & 64 & 128 & 256 \\
        \midrule
        Private key size $\text{privlen}_{\text{bits}}/8$ (bytes) & 96 & 184 & 360 \\
        Public key size $\text{publen}_{\text{bits}}/8$ (bytes) & 450 & 1024 & 2440 \\
        Signature size $\text{siglen}_{\text{bits}}/8$ (bytes) & 249 & 555 & 1221 \\
        \bottomrule
    \end{tabular}
\end{table}
\todo{Insert relevant parameters here}

\subsection{Hawk key pairs and key pair generation}
A Hawk private key is represented by the matrix
\[ \mat{B} = 
    \begin{bmatrix} 
        f & F \\
        g & G
    \end{bmatrix}
    \in \mathcal{K}_{n}^{2 \times 2}
\]
Here, entries are chosen such that $f$ and $g$ have small coefficients, and the equation $fG - Fg = 1 \mod X^{n} + 1$ holds, and consequently $\det(\mat{B}) = 1$, making $\mat{B}$ invertible.
The inverse of $\mat{B}$ is 
\[
    \mat{B}^{-1} =
    \begin{bmatrix}
        G & -F \\
        -g & f
    \end{bmatrix}
    \in \mathcal{K}_{n}^{2 \times 2}
\]
A Hawk public key is defined as 
\[
    \mat{Q} = 
    \begin{bmatrix}
        q_{00} & q_{01} \\
        q_{10} & q_{11}
    \end{bmatrix}
    =
    \mat{B}^* \mat{B}
    =
    \begin{bmatrix}
        f^* f + g^*g & f^* F + g^*G \\
        F^* f + G^*g & F^*F + G^*G
    \end{bmatrix}
\]
where $f^*$ denotes the Hermitian adjoint of $f$, explicitly $f^* = f_0 - f_{n-1}X - \cdots - f_{1}X^{n-1}$,
and $\mat{B}^*$ is the transpose of $\mat{B}$, $\mat{B}^T$ where each entry is taken the Hermitian adjoint of. Explicitly:
\[
    \mat{B}^* = 
    \begin{bmatrix}
        f^* & g^* \\
        F^* & G^*
    \end{bmatrix}
\]
We can also define $\mathsf{rot}$ on a matrix as the mapping 
\[\mathsf{rot}: \mathcal{K}_n^{2 \times 2} \rightarrow \bb{Q}^{2n \times 2n}, \ 
    \mathsf{rot}(
    \begin{bmatrix}
        f & F \\
        g & G
    \end{bmatrix}
    )
    =
    \begin{bmatrix}
        \mathsf{rot}(f) & \mathsf{rot}(F) \\
        \mathsf{rot}(g) & \mathsf{rot}(G)
    \end{bmatrix}
\]

$\mathsf{rot}(\mat{B})$ serves as a basis for the private lattice in which a (digest of a) message will be signed in the signature generation step.
A simplified version of the key generation algorithm is described in the following algorithm:
\begin{algorithm}[H]\label{Simplified Hawk Key Generation}
\caption{Simplified Hawk Key Generation}
\begin{algorithmic}[1]
    \State Sample $f, g \in \bb{Z}[X] / (X^n + 1)$ from $\mathsf{bin}(\eta)$
    \State Compute $F, G$ s.t. $fG - Fg = 1 \mod \bb{Z}[X] / (X^n + 1)$ holds
    \State $\mat{B} \gets \begin{bmatrix} f & F \\ g & G \end{bmatrix}$
    \State $\mat{Q} \gets \mat{B}^* \mat{B}$
    \State \Return private key $\mat{B}$, public key $\mat{Q}$
\end{algorithmic}
\end{algorithm}
\subsection{Solving the NTRU-equation}
An important point in the key generation process is finding proper polynomials $F$ and $G$ that satisfy the NTRU-equation $fG - Fg = 1 \mod \bb{Z}[X] / (X^n + 1)$.
Importantly, coefficients of $F$ and $G$ need to be rather small, and the procedure of solving the equation is a time-consuming part of the key generation process. 
\todo{Need some explanation of resultants here}
In the original NTRU system (both encryption and signature) resultants are used. Hawk uses the method proposed by Pornin and Prest in \cite{PP19} which improves upon the existing
resultant method in terms of both time- and memory complexity.

\subsection{Discrete Gaussian Distribution}
Before introducing the Hawk signature generation we describe the procedure to sample from the Discrete Gaussian Distribution, as described in \cite{HawkSpec24}. \\
Denote by $\dgd_{2\bb{Z} + c, \sigma }$ the Discrete Gaussian Distribution with parameter $c$ and $\sigma$.
Let $\rho_{\sigma}: \bb{Z} \rightarrow \bb{R}, \rho_{\sigma}(x) = \exp(\frac{-x^2}{2\sigma^2})$.
The Probability Density Function (PDF) of $\dgd_{2\bb{Z} + c, \sigma }$ is defined as:
\[
    \text{Pr[X = x] } = \frac{\rho_{\sigma}(x)}{\mathlarger{\sum_{y \in 2\bb{Z} + c} \rho_{\sigma}(y)}}
\]
For $z \geq 0$ we define the function $P_c(z) = \text{Pr}[ |X| \geq z ]$ when $X \sim \dgd_{2\bb{Z}+c, \sigma}$.
Using this function for $c \in {0, 1}$, we compute two Cumulative Distribution Tables (CDT) $T_0$ and $T_1$
such that $T_0[k] = P_0(2+2k)$ and $T_1[k] = P_1(3+2k)$ where $T_c[k]$ denotes the $k$-th index in the table.
In practice, to avoid using floating point numbers, the entries in the table is scaled by $2^{78}$ such that 
entries are integers with a high enough precision. For this overview, however, we only consider the unscaled version.
Using the tables, we can define a procedure $\mathsf{sample}$ given by the following algorithm:

\begin{algorithm}[H]
% \caption{Simplified, unscaled sampling from $\dgd_{2\bb{Z}+c, \sigma}$ }
\caption{$\mathsf{sample}$}
\begin{algorithmic}[1]
    \Require{parameter $c \in {0, 1}$}
    \State $q \gets$ uniformly sampled from $[-1, 1] \in \bb{R}$
    \State $z \gets 0$
    \While{$T_c[z] \neq 0$}
    \If{$|q| \leq T_c[z]$}
    \State $z \gets z + 1$
    \Else
    \State $z \gets 2z + c$
    \If{$q < 0$}
    \State $z \gets -z$
    \EndIf
    \EndIf
    \EndWhile
    \State \Return $z$
\end{algorithmic}
\end{algorithm}

This algorithm only samples one point given parameter $c$.
We can extend this to generate vectors of length $n$ where each entry is distributed according to $\dgd_{2\bb{Z}+c, \sigma}$ by the following procedure:
\begin{algorithm}[H]
\caption{Sample vector of length n according to $\dgd_{2\bb{Z}+c, \sigma}$}
\begin{algorithmic}[1]
    \Require{Binary vector $\vec{t}$ with entries uniformly distributed from ${0,1}$}
    \State $\vec{x} \gets$ empty vector of length $2n$
    \For{$i = 0,1,..., 2n -1$}
    \State $\vec{x}[i] \gets \mathsf{sample}(\vec{t}[i])$
    \EndFor
    \Return $\vec{x}$
\end{algorithmic}
\end{algorithm}

In this manner, one can sample a lattice point $\vec{x}$ which is "close" to a target lattice point $\vec{t}$, which will be used in the signature generation step.

\subsection{Hawk signature generation}
To generate a Hawk signature of a message $\vec{m}$, one computes a hash digest $\vec{h}$ of the message, and samples a point $\vec{x}$ that is close to $\vec{h}$ in the 
private lattice generated by $\mathsf{rot}(\mat{B})$. By transforming the point $\vec{x}$ back to the lattice $\bb{Z}^{2n}$ via $\mat{B}^{-1}$ one has a signature that can be verified 
by anyone that has access to the public key $\mat{Q}$.
Below is the (simplified) procedure formulated as an algorithm:
\begin{algorithm}
\caption{Simplified Hawk Signature Generation}
\begin{algorithmic}[1]
    \Require{Message $\vec{m}$, private key $\mat{B}$}
    \State $M \gets H(\vec{m})$ \Comment{H is a hash function}
    \State $\vec{h} \gets H(M || \mathsf{salt})$ \Comment{$\mathsf{salt}$ is a randomly generated value and $||$ denotes concatenation}
    \State $\vec{t} \gets \mat{B} \vec{h} \mod 2$ \Comment{Reduction $\mod 2$ is done entrywise}
    \State $\vec{x} \gets \mathsf{sample}(\vec{t})$
    \State restart if $\lVert \vec{x} \rVert ^2$ is too high
    \State $\vec{w} \gets \mat{B}^{-1} \vec{x}$
    \State $\vec{s} \gets \frac{1}{2}(\vec{h} - \vec{w})$
    \State \Return signature $\vec{s}$, salt $\mathsf{salt}$
\end{algorithmic}
\end{algorithm}
\subsection{Hawk signature verification}
To verify a Hawk signature, one simply recomputes the vector $\vec{h}$ and in turn the vector $\vec{w}$, and check if the $\mat{Q}$-norm of $\vec{w}$,
$\lVert \vec{w} \rVert_{\mat{Q}}^2$ is not too high. A signature with $\mat{Q}$-norm of appropriately short length will be considered valid.
A summary of the simplified procedure is given in the following algorithm:

\begin{algorithm}
\caption{Simplified Hawk Signature Verification}
\begin{algorithmic}[1]
    \Require{Signature $\vec{s}$, message $\vec{m}$, salt $\mathsf{salt}$, public key $\mat{Q}$ }
    \State $M \gets H(\vec{m})$ 
    \State $\vec{h} \gets H(M || \mathsf{salt})$
    \State $\vec{w} \gets \vec{h} - 2\vec{s}$
    \If{$\lVert \vec{w} \rVert_{\mat{Q}}^2$ is low enough}
    \State \Return true
    \Else \ \Return false
    \EndIf
\end{algorithmic}
\end{algorithm}
\subsection{Hawk security}
\section{Implementation of Hawk}
